---
title: "How to Use ezpickr"
author: "JooYoung Seo"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to Use ezpickr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# ezpickr: Convenient Package/Function for Choosing Any Rectangular Data File Using Interactive GUI Dialog Box, and Seamlessly Manipulating Tidy Data between an Excel Window and R Session

[![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)](http://www.gnu.org/licenses/gpl-3.0)
[![CRAN status](https://www.r-pkg.org/badges/version/ezpickr)](https://cran.r-project.org/package=ezpickr)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![Travis build status](https://travis-ci.org/jooyoungseo/ezpickr.svg?branch=master)](https://travis-ci.org/jooyoungseo/ezpickr)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/jooyoungseo/ezpickr?branch=master&svg=true)](https://ci.appveyor.com/project/jooyoungseo/ezpickr)
[![Codecov test coverage](https://codecov.io/gh/jooyoungseo/ezpickr/branch/master/graph/badge.svg)](https://codecov.io/gh/jooyoungseo/ezpickr?branch=master)
      
The goal of ezpickr is to provide R beginners with a convenient way to pick up their data files in a tidy tibble form into an R environment using GUI file-picker dialogue box (`ezpickr::pick()`), and to open and manipulate their data objects using Excel application for a seamless data communication between an Excel and R session (`ezpickr::viewxl()`).

You can alternatively use `ezpickr::pick()` function for choosing *.csv, *.csv2, *.tsv, *.txt, *.xls, *.xlsx, *.json, *.html, *.htm, *.php, *.pdf, *.doc, *.docx, *.rtf, *.RData, *.Rda, *.RDS, *.sav (SPSS), *.por, *.sas7bdat, *.sas7bcat, *.dta, *.xpt, *.mbox, and *.Rmd files in an interactive GUI mode A file choose dialog box will be prompted.

Any additional arguments available for each file type and extension: `vroom::vroom()` for 'CSV' (Comma-Separated Values); 'CSV2' (Semicolon-Separated Values); 'TSV' (Tab-Separated Values)'txt' (plain text) files; `readxl::read_excel()` for 'Excel' files; `haven::read_spss()` for 'SPSS' files; `haven::read_stata()` for 'Stata' files; `haven::read_sas()` for 'SAS' files; `textreadr::read_document()` for 'Microsoft Word', 'PDF', 'RTF', 'HTML', 'HTM', and 'PHP' files; `jsonlite::fromJSON()` for 'JSON' files; `mboxr::read_mbox()` for 'mbox' files; `rmarkdown::render()` for 'Rmd' files; `base::source()` for 'R' files; `base::readRDS()` for 'RDS' files; `base::load()` for 'RDA' and 'RDATA' files.

Each corresponding function depending upon a file extension will be automatically matched and applied once you pick up your file using either the GUI-file-chooser dialog box or explicit path/to/filename.

## Installation

### Development Version

You can install the latest development version as follows:

```{r, eval=F}
if(!require(remotes)) {
install.packages("remotes")
}

remotes::install_github('jooyoungseo/ezpickr')
```

### Stable Version

You can install the released version of ezpickr from [CRAN](https://CRAN.R-project.org) with:

```{r, eval=F}
install.packages("ezpickr")
```

## Example

### Usage of the `pick()` Function

This is a basic example which shows you how to import data files:

```{r example1, eval=F}
library(ezpickr)

# Choosing file and saving it into a variable
## Scenario 1: Picking up a file using interactive GUI dialog box:
data <- pick() ## Please use `picko()` instead if your path/file contains any Korean characters.

## Scenario 2: Picking up a file using an explicit file name ("test.sav" in the example below; however, you can feed other files through this function such as *.SAS, *.DTA, *.csv, *.csv2, *.tsv, *.xlsx, *.txt, *.html, webpage URL, *.json, *.Rda, *.Rdata, and more):
data <- pick("test.sav") ## Please use `picko("test.sav")` instead if your path/file contains any Korean characters.

# Now you can use the imported file as a tibble data frame.
str(data)
```

### Usage of the `viewxl()` Function

You can open any data.frame, tibble, matrix, table or vector from an R session into your default-set spreadsheet application window as follows:

```{r example2, eval=F}
library(ezpickr)

data(airquality)
str(airquality)

# Use `viewxl()` function to open your data object in your spreadsheet:
viewxl(airquality)
# Then, when necessary, you can modify the opened data in the spreadsheet and save it as a new data.

# You can pass a list object to the `viewxl()` function like below:
l <- list(iris = iris, mtcars = mtcars, chickwts = chickwts, quakes = quakes)
viewxl(l)
# Then, each list item will appear in your Excel window sheet by sheet.
```
