---
title: "How to Use ezpickr"
author: "JooYoung Seo"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to Use ezpickr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Convenient Function for Choosing Any Rectangular Data File Using Interactive GUI Dialog Box

You can alternatively use this function for choosing *.csv, *.csv2, *.tsv, *.txt, *.xls, *.xlsx, *.json, *.html, *.htm, *.php, *.pdf, *.doc, *.docx, *.rtf, *.RData, *.Rda, *.RDS, *.sav (SPSS), *.por, *.sas7bdat, *.sas7bcat, and *.dta files in an interactive GUI mode A file choose dialog box will be prompted.

Any additional arguments available for each file type and extension: `readr::read_csv()` for CSV (Comma-Separated Values) files; `readr::read_csv2()` for CSV2 (Semicolon-Separated Values) files; `readr::read_tsv()` for 'TSV' (Tab-Separated Values) files; `readr::read_file()` for 'txt' (plain text) files; `readxl::read_excel()` for 'Excel' files; `haven::read_spss()` for 'SPSS' files; `haven::read_stata()` for 'Stata' files; `haven::read_sas()` for 'SAS' files; `textreadr::read_document()` for 'Microsoft Word', 'PDF', 'RTF', 'HTML', 'HTM', and 'PHP' files; `jsonlite::fromJSON()` for 'JSON' files; `base::readRDS()` for 'RDS' files; `base::load()` for 'RDA' and 'RDATA' files.

Each corresponding function depending upon a file extension will be automatically matched and applied once you pick up your file using either the GUI-file-chooser dialog box or explicit path/to/filename.

Once you pick up your rectangular data file using `pick()` function, a tidy tibble (table data.frame) object will be returned automatically for your further analysis.

# Installation

## Development Version

You can install the latest development version as follows:

```{r, eval=F}
if(!require(devtools)) {
install.packages("devtools")
}

devtools::install_github('jooyoungseo/ezpickr')
```

## Stable Version

You can install the released version of ezpickr from [CRAN](https://CRAN.R-project.org) with:

```{r, eval=F}
install.packages("ezpickr")
```


# Basic Usage

In order to use ezpickr do the folowing:

```{r, eval=F}
library(ezpickr)
# Choosing file and saving it into a variable
## Scenario 1: Picking up a file using interactive GUI dialog box:
data <- pick()

## Scenario 2: Picking up a file using an explicit file name ("test.sav" in the example below; however, you can feed other files through this function such as *.SAS, *.DTA, *.csv, *.csv2, *.tsv, *.xlsx, *.txt, *.html, webpage URL containing table, *.json, *.Rda, *.Rdata, and more):
data <- pick("test.sav")

# Now you can use the imported file as a data frame.
str(data)
```
